Investigating motor vehicle collisions in Toronto: Installing more red light cameras do not stop traffic accidents from happening

### 2022-02-05 outputs/paper/paper.Rmd
finalize data

---
title: "Investigating motor vehicle collisions in Toronto: Installing more red light cameras do not stop traffic accidents from happening"
author: 
  - Alicia Yang
thanks: "Code and data are available at: https://github.com/Alicia-y/Telling-stories-with-data."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Vehicle collisions occur constantly in big citys. They sometimes could be severe issues when resulting in damage in public and personal properties, injuries, or even death. This report aims to investigate motor vehicle collisions in Toronto that result in injuries or deaths from 2006 to 2020. By exploring the trend of these traffic collisions in respect of their frequency, fatality, and location, I find that the total number of accidents has a descending trend. However, the number of vehicle collisions that occurred at intersections has not reduced despite the fact that more red light cameras are installed. This finding suggests that ... furthur measures should be taken to enhance the safety issue on road."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

As one of the busiest and most modern city in Canada, Toronto constantly faces a large number of citizens, and, inevitably, heavy traffic. The road condition in Toronto is busy most of the time. The vast majority of roads and buildings under construction that take place almost everywhere narrow the roadway of vehicles and turn off traffic lights. Heavy traffic is likely to be one of the main reasons behind car accidents, because it increases the road rage and encourages the vehicle drivers to make dangerous moves to save time. Vehicle collisions have always brought large financial costs to the involving parties, and even more, they even brought injuries and deaths. In just 2019, traffic accidents resulted in more than 1700 deaths and more than 140000 injuries.

@@

By comparing Figure 3 and Figure 4, I found that they haven't show any associations between the number of traffic accidents and the number of red light cameras installed.

@@

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

@@

## Weaknesses and next steps

@@

https://tc.canada.ca/en/road-transportation/statistics-data/canadian-motor-vehicle-traffic-collision-statistics-2019

>>>>

---
title: "Investigating motor vehicle collisions in Toronto: Installing more red light cameras do not stop traffic accidents from happening"
author: 
  - Alicia Yang
thanks: "Code and data are available at: https://github.com/Alicia-y/Telling-stories-with-data."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "Vehicle collisions occur constantly in Toronto and sometimes could be severe when resulting in damage in public and personal properties, injuries, or even death. This report aims to investigate motor vehicle collisions in Toronto that result in injuries or deaths from 2006 to 2020. By exploring the trend of these traffic collisions in respect of their frequency, fatality, and location, I find that the total number of accidents has a descending trend. However, the number of vehicle collisions that occurred at intersections has not reduced despite the fact that more red light cameras are installed. This finding suggests that unlike, ...... doesn't prevent traffic accidents at intersection, furthur measures should be taken to enhance the safety issue on road."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

@@

As one of the busiest and most modern city in Canada, Toronto constantly faces a large number of citizens, and, inevitably, heavy traffic. The road condition in Toronto is busy most of the time. The vast majority of roads and buildings under construction that take place almost everywhere narrow the roadway of vehicles and turn off traffic lights. Heavy traffic is likely to be one of the main reasons behind car accidents, because it increases the road rage and encourages the vehicle drivers to make dangerous moves to save time. Vehicle collisions have always brought large financial costs to the involving parties, and even more, they even brought injuries and deaths. In just 2019, traffic accidents resulted in more than 1700 deaths and more than 140000 injuries [@cite1].

@@

By comparing Figure 3 and Figure 4, I found that they haven't show any associations between the number of traffic accidents and the number of red light cameras installed. For instance, Scarborough has installed the most number of red light cameras, especially after the year of 2016, but its number of traffic accidents didn't reduced at all, it even reach its peak in 2018, nor did the fatality of those accidents. We see a large decrease in Toronto and East York's motor vehicle collisions, but it didn't installed at much red cameras as Etobicoke York or Scarborough.

@@

No relationships
No increase non decrease

@@

## Limitations

@@
